---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{shinycurate}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> [!WARNING]  
> This package was designed for local use only, we do not reccomend hosting remotely.
> This package is in early development and not yet ready for use


Use a shiny app to look through set of text, manually enter values based on the curation of the text.

## Installation

You can install the development version of `{shinycurate}` like so:

```r
if (!require("remotes"))
    install.packages("remotes")

remotes::install_github("selkamand/shinycurate")
```

## Quick Start

You can launch the application by running:

```{r, eval = FALSE}
create_database(path = "mydb.sqlite", template = c(id="TEXT", ncells = "INTEGER", cellproportion = "REAL"))

shinycurate::run_app()
```

Then you'll need to upload 

1) a two column data.frame with colums (id, text). 
2) A database to store your curation results. 

You can generate this using the `create_database()` function.
